---
title: "R Project 1 - Hello R"
author: "Neandrea Lee"
date: "Due Sept 8th"
output: 
  html_document: 
    fig_width: 9
    fig_height: 7
    highlight: pygments
---

MAKE SURE YOU READ AND FOLLOW **ALL** INSTRUCTIONS ON THE INSTRUCTION DOCUMENT. 

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

1836 rows and 2 columns

### Exercise 2

First let's plot the data in the dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

In this exercise we code the x y plots for star set

```{r plot-star}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

We now calculate the x y correlation for the star data set
 
```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))
```
The sizes are that far off, with a 0.0015 diff but r dino is larger

### Exercise 4

Here we have added code for the x y circle set

```{r plot-circle}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")
ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()
```
Last but not least we calculate the correlation of x y for circle 

```{r cor-circle}
circle_data %>%
  summarize(r = cor(x, y))
```
The sizes are that far off, with a 0.0038 diff but r circle is larger

### Exercise 5

Finally we plot all the data sets together

```{r plot-all data sets}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset))+ 
  geom_point()+
  facet_wrap(~ dataset, ncol = 3) +
  theme(legend.position = "none")

```
Final correlation coefficient of all data sets

```{r}
datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x, y)) %>%
  print(13)
```

